% =====
% Talks
% =====


% colloquium macro
% #1: Date
% #2: Title
% #3: University
% #4: Department
% #5: City
% #6: Invited/Submitted
\newcommand{\colloquium}[6]{
    #1 & #3 \newline #4 & \textit{#2} & #6\\
}

%\centering
\begin{tabularx}{\linewidth}{lX}
    \heading{Scholarly Presentations}
    \multicolumn{2}{l}{\emph{Entries are limited to the three years 2021, 2022, \& 2023}}\\\addlinespace
\end{tabularx}

\begin{tabularx}{\linewidth}{llXXl}
  \addlinespace
  \addlinespace
  \multicolumn{4}{l}{\bfseries\sffamily Colloquia}\\
  \addlinespace

  \midrule
  ID & Date & Venue & Title & Type \\
  \midrule

  \annualreview{}CQ5. & \colloquium{2023-03-16}{From Tools to Teammates: Building machines that understand humans}%
            {University of Arizona}%
            {School of Information}%
            {Tucson, AZ}%
            {Invited}

  \annualreview{}CQ4. & \colloquium{2023-01-27}{Artificial Social Intelligence}%
            {University of Arizona}%
            {School of Information}%
            {Tucson, AZ}%
            {Research Blitz}

  \annualreview{}CQ3. & \colloquium{2021-12-09}{Theory of Mind-based Cognitive Architecture for Teams}%
            {University of Arizona}%
            {School of Information}%
            {Tucson, AZ}%
            {Research Blitz}

  CQ2. & \colloquium{2020-10-08}{Building machines that understand humans}%
            {University of Arizona}%
            {Systems and Industrial Engineering}%
            {Tucson, AZ}%
            {Invited}

  CQ1. & \colloquium{2020-09-04}%
        {Building machines that understand humans}%
        {University of Arizona}%
        {Cognitive Science Colloquium Series}%
        {Tucson, AZ}%
        {Invited}

\end{tabularx}

\begin{tabularx}{\linewidth}{llXXll}
  \addlinespace
  \addlinespace
  \multicolumn{5}{l}{\bfseries\sffamily Conferences}\\
  \addlinespace
  \midrule
  ID & Date & Venue & Title & City & Type\\
  \midrule

  CP6. & \talk{2019}{Eidos, INDRA, \& Delphi: From Free Text to Executable Causal Models}%
               {TRIPODS 2nd Southwest Summer Conference}
               {Tucson, AZ}
               {Submitted}
  CP5. & \talk{2016}{A Razor Search for Dark Matter at a Future 100 TeV Collider}%
               {Joint Meeting of the Four Corners and Texas Sections of the American Physical Society}
               {Las Cruces, NM}
               {Submitted}
  CP4. & \talk{2015}{Light Charged Higgs Bosons in Single-Top Production}%
               {Phenomenology 2015 Symposium}
               {Pittsburgh, PA}
               {Submitted}
  CP3. & \talk{2015}{Light Charged Higgs Bosons in Two Higgs Doublet Models}%
               {Annual Meeting of the APS Four Corners Section}
               {Tempe, AZ}
               {Submitted}
  CP2. & \talk{2014}{Light Charged Higgs Bosons in Single-Top Production}%
               {Annual Meeting of the APS Four Corners Section}
               {Orem, UT}
               {Submitted}
  CP1. & \talk{2014}{Light Charged Higgs Bosons to AW/HW via Top Decay}%
               {23$^{\text{rd}}$ International Conference on Supersymmetry and Unification of Fundamental Interactions}
               {Lake Tahoe, CA}
               {Submitted}
\end{tabularx}

\begin{tabularx}{\linewidth}{lX}
    \subheading{Posters}
    \publication{\annualreview{}P5.}{Erikson_Pyarelal:2022b}
    \publication{\annualreview{}P4.}{Erikson_Pyarelal:2022a}
    \publication{\annualreview{}P3.}{Erikson_Pyarelal:2021}
    \publication{\annualreview{}P2.}{Schoelen:2021}
    \publication{P1.}{Morrison:2020}

\end{tabularx}
