\begin{ctabular}{rp{5.6in}}
    \heading{Works in Progress}
    \multicolumn{2}{p{5.6in}}{%
        \itshape
        \begin{itemize}
            \item Co-authors who are student advisees or postdoctoral mentees
                have a $^\circ$ next to their names.
            \item Items with an \inrank{} to their left correspond to activities
                performed in rank.
            \iftoggle{apr}{%
            \item Items with an \annualreview{} to their left correspond to
                entries in the last three calendar years (for the annual review
                process).
            }{}
        \end{itemize}
    }\\\addlinespace

    \subheading{Manuscripts under review}
    \publication{\inrank{}MR4.}{Erikson.ea:2024}
    \publication{\inrank{}MR3.}{Zhang.ea:2024}
    \publication{\inrank{}\annualreview{}MR2.}{Pyarelal.ea:2024}
    \publication{\inrank{}\annualreview{}MR1.}{Soares.ea:2024}

    \subheading{Manuscripts in preparation and preprints}
    \multicolumn{2}{p{5.6in}}{%
        \emph{%
            Preprints are non-refereed papers that have been made public.
            They are also technically `manuscripts in preparation',
            since they are earlier versions of manuscripts that are in the
            process of being revised and resubmitted.
            Manuscripts in preparation that have an associated preprint have
            names in blue, indicating they are clickable links that link to
            their corresponding arXiv page. For preprints, the listed year is
            the year that the preprint was uploaded. However, these papers are
            typically currently under preparation for resubmission.
        }
    }\\\addlinespace
    \addlinespace
    \publication{\annualreview{}\inrank{}MP3.}{KC.ea:2024}
    \publication{\annualreview{}\inrank{}MP2.}{Basavaraj.ea:2022}
    \publication{\annualreview{}\inrank{}MP1.}{Zhang.ea:2022b}

\end{ctabular}
